Qualifying Report

### 2019-01-30 Source/QualifyingReport/QualifyingReport.tex
edits to QR

% Muangpaisan - Digit span and verbal fluency tests in patients with MCI and normal subjects in Thai community.

@@

Among those with no disorder in cognition, mobility and mood, being in the lowest DSST quartile compared to the highest was associated with nearly twice the odds of developing one or more clinical or subclinical disorders. Associations were stronger for incident clinical disorders in cognition. Slower psychomotor speed may serve as a biomarker of risk of clinical disorders, mobility and mood. While in part attributable to vascular brain disease, other potentially modifiable contributors may be present \cite{Rosano2016}. Further studying the causes of psychomotor slowing with ageing might provide novel insights into age-related brain disorders. Pascoe compared patients with PD with Normal Cognition (PD-N) with those with PD and MCI (PD-MCI) and healthy participants. PD-MCI pariticipants achieved significantly lower scores than other groups in the DSST task \cite{Pascoe2018}.

@@

% CITE - Taylor 1969 1979 - Variants
% CITE - Strauss - A comparison of the Rey and Taylor figures

@@

Inhibitory deficits are a common in all stages of dementia. This is usually tested using Stroop test, however this has the drawback of lacking ecological validity. Therefore researchers have moved towards using the Hayling Sentence Completion Test (HCST) which uses skills such as word retreval as well as the ability to inhibit ones responses where appropriate and is therefore a much more ecologically valid task. There are two parts to the HCST. In the first part, participants have to complete a sentence by providing a word that best fits the given sentence (this is known as the initiation condition). In this second part, participants have to complete sentences by inhibiting an impulse to give the word that best first the sentence as in the first part, and producing a semantically unconnected word. Performance in both conditions is measured by the time taken for the participant to initiate a response, and in the inhibition condition also by the correctness of the word.   

@@

Martyr et al compared healthy controls with patients with dementia and patients with parkinson's disease \cite{Martyr2017}. They found that a high proportion of Category A errors (producing a word that fits the sentence when instructed otherwise) was a factor in performance loss for participants with dementia. Findings suggest that the HSCT may be sensitive to verbal suppression deficits and may provide insight into inhibitory control in participants with dementia. Patients with Dementia were significantly slower than controls in the initiation and inhibition conditions vs healthy controls, and slower than patients with parkinsons disease in the initiation but not the inhibition condition.

@@

Darweesh et al, used the Purdue Pegboard Test to assess manual dexterity in a healthy older adult population and followed their participants for between eight and twelve years until an indication of the onset of a neurodegenerative disease \cite{Darweesh2017}. In this time 227 (4\%) of their participants went on to develop a diagnosis of dementia. They noted that higher PPT scores were associated with lower risk of incident neurodegnerative disease and noted significant associations of PPT scores with all forms of dementia and this potentially highlights a deterioration of motor function in the pre-clinical  phase of dementia.

@@

% Describe the test

@@

% CITE RILEY!

@@

\subsubsection{Natural Language Toolkit}
% CITE Bird, Steven, Edward Loper and Ewan Klein (2009). Natural Language Processing with Python.  O'Reilly Media Inc.
The Natural Language Toolkit (NLTK) was originally designed as part of a computational linguistics course but has evolved to become an open-source framework which includes methods and modules for a wide array of Natural Language tasks (see Table 2.2 for a full list) \cite{Bird2009}.

@@

@@

\begin{table}
	\begin{center}
	\begin{tabular}{ | p{3cm} | p{3cm} | p{3cm} | p{3cm} |}
		\hline
		& RR & GHWB & DJT \\ \hline
		Unique Words & 894.13 (85.15) & 667.76 (218.67) & 481.82 (221.29) \\ \hline
		Non Specific Nouns & 12.72 (4.63) & 6.78 (4.32) & 7.41 (8.75) \\ \hline
		LI Verbs & 124.22 (17.89 )& 103.45 (51.87) & 84.48 \\ \hline
		Nouns Normalised & 124.22 (17.89 )& 103.45 (51.87) & 84.48 \\ \hline
		Verbs Normalised & 124.22 (17.89 )& 103.45 (51.87) & 84.48 \\ \hline
		Adjectives Normalised & 124.22 (17.89 )& 103.45 (51.87) & 84.48 \\ \hline
		Adverbs Normalised & 124.22 (17.89 )& 103.45 (51.87) & 84.48 \\ \hline
		Pronouns Normalised & 124.22 (17.89 )& 103.45 (51.87) & 84.48 \\ \hline
		Conjunctions Normalised & 124.22 (17.89 )& 103.45 (51.87) & 84.48 \\ \hline
		Prepositions Normalised & 124.22 (17.89 )& 103.45 (51.87) & 84.48 \\ \hline
		Interjections Normalised & 124.22 (17.89 )& 103.45 (51.87) & 84.48 \\ \hline

	\end{tabular}
	\caption{\label{tab:table-name}Pearson Correlations for Features}
	\end{center} 
\end{table}

@@

\appendix
\section{Title of Appendix A}
Text of Appendix A is Here

\section{Title of Appendix B}
Text of Appendix B is Here

\section{Title of Appendix C}
Text of Appendix C is Here.

>>>>

@@

Among those with no disorder in cognition, mobility and mood, being in the lowest DSST quartile compared to the highest was associated with nearly twice the odds of developing one or more clinical or subclinical disorders. Associations were stronger for incident clinical disorders in cognition. Slower psychomotor speed may serve as a biomarker of risk of clinical disorders, mobility and mood. While in part attributable to vascular brain disease, other potentially modifiable contributors may be present \cite{Rosano2016}. Further studying the causes of psychomotor slowing with ageing might provide novel insights into age-related brain disorders. Pascoe compared patients with PD with Normal Cognition (PD-N) with those with PD and MCI (PD-MCI) and healthy participants. PD-MCI participants achieved significantly lower scores than other groups in the DSST task \cite{Pascoe2018}.

@@

@@

Inhibitory deficits are a common in all stages of dementia. This is usually tested using Stroop test, however this has the drawback of lacking ecological validity. Therefore researchers have moved towards using the Hayling Sentence Completion Test (HCST) which uses skills such as word retrieval as well as the ability to inhibit ones responses where appropriate and is therefore a much more ecologically valid task. There are two parts to the HCST. In the first part, participants have to complete a sentence by providing a word that best fits the given sentence (this is known as the initiation condition). In this second part, participants have to complete sentences by inhibiting an impulse to give the word that best first the sentence as in the first part, and producing a semantically unconnected word. Performance in both conditions is measured by the time taken for the participant to initiate a response, and in the inhibition condition also by the correctness of the word.   

@@

Martyr et al compared healthy controls with patients with dementia and patients with Parkinson's disease \cite{Martyr2017}. They found that a high proportion of Category A errors (producing a word that fits the sentence when instructed otherwise) was a factor in performance loss for participants with dementia. Findings suggest that the HSCT may be sensitive to verbal suppression deficits and may provide insight into inhibitory control in participants with dementia. Patients with Dementia were significantly slower than controls in the initiation and inhibition conditions vs healthy controls, and slower than patients with Parkinson's disease in the initiation but not the inhibition condition.

@@

Darweesh et al, used the Purdue Pegboard Test (PPT) to assess manual dexterity in a healthy older adult population and followed their participants for between eight and twelve years until an indication of the onset of a neurodegenerative disease \cite{Darweesh2017}. In this time 227 (4\%) of their participants went on to develop a diagnosis of dementia. They noted that higher PPT scores were associated with lower risk of incident neurodegnerative disease and noted significant associations of PPT scores with all forms of dementia and this potentially highlights a deterioration of motor function in the pre-clinical  phase of dementia.

@@

@@

@@

\subsubsection{Natural Language Toolkit}
The Natural Language Toolkit (NLTK) was originally designed as part of a computational linguistics course but has evolved to become an open-source framework which includes methods and modules for a wide array of Natural Language tasks (see Table 2.2 for a full list) \cite{Bird2009}.

@@

% CITE Bird et al 2000 The Rise and Fall of Frequency and Imageability Noun and Verb Production in Semantic Dementia

@@

\begin{table}
	\begin{center}
	\begin{tabular}{ | p{3cm} | p{3cm} | p{3cm} | p{3cm} |}
		\hline
		& RR & GHWB & DJT \\ \hline
		Unique Words & -0.58 & -0.25 & 0.16 \\ \hline
		Non Specific Nouns & 0.25 & -0.08 & -0.03 \\ \hline
		LI Verbs & -0.23 & -0.20 & 0.02 \\ \hline
		Nouns Normalised & -0.692 & -0.03 & 0.02 \\ \hline
		Verbs Normalised & 0.32 & 0.24 & -0.03 \\ \hline
		Adjectives Normalised & -0.38 & 0.08 & -0.34 \\ \hline
		Adverbs Normalised & 0.38 & 0.02 & -0.36 \\ \hline
		Pronouns Normalised & 0.63 & 0.13 & 0.12 \\ \hline
		\multicolumn{4}{@{}p{1.5in}}{\footnotesize (\,) * denotes p < 0.05} \\
    	\multicolumn{4}{@{}p{1.5in}}{\footnotesize [\,] ** denotes p < 0.01} \\
    	\multicolumn{4}{@{}p{1.5in}}{\footnotesize [\,] *** denotes p < 0.001} \\
	\end{tabular}
	\caption{\label{tab:table-name}Pearson Correlations for Features}
	\end{center} 
\end{table}

@@
